\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.6cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0em}
  {}
  [\titlerule]

\begin{document}

% ================= HEADER =================
{\LARGE \textbf{Vinicius Abreu}} \\[4pt]
Senior Backend Engineer \& Tech Lead $|$ APIs, Microservices \& Distributed Systems \\[6pt]

\href{mailto:vinicius.abreu262@gmail.com}{vinicius.abreu262@gmail.com} $|$
\href{https://www.linkedin.com/in/vs-abreu/}{LinkedIn} $|$
\href{https://github.com/vinnedev}{GitHub} \\[10pt]

% ================= SUMMARY =================
\section*{Summary}
Software Engineer with 5+ years of hands-on experience building, maintaining, and evolving backend systems focused on APIs, microservices, performance, reliability, and clean architecture. Currently Lead Software Engineer at Celeste AI, driving technical decisions across backend, cloud, CI/CD, and production support. Strong record of turning complex requirements into simple, stable, and scalable solutions. Main stack: Node.js, TypeScript, Go, Python, PostgreSQL, Terraform, Azure DevOps, and AWS.

% ================= SKILLS =================
\section*{Technical Skills}
\textbf{Languages:} TypeScript, Node.js, Go, Python, Java \\[3pt]
\textbf{Backend \& Messaging:} RESTful APIs, Microservices, Distributed Systems, Event-driven Architecture, RabbitMQ \\[3pt]
\textbf{Databases:} PostgreSQL, SQL Server, MySQL, MongoDB \\[3pt]
\textbf{Cloud \& DevOps:} AWS, Azure, GCP, Terraform, Docker, Kubernetes, CI/CD, Azure DevOps \\[3pt]
\textbf{Engineering:} System Design, Clean Architecture, Observability, Performance, Resilience, Idempotency \\[3pt]
\textbf{Legacy:} Delphi 2010

% ================= EXPERIENCE =================
\section*{Experience}

\textbf{Celeste AI} — Lead Software Engineer \hfill Jul 2025 – Present \\
Remote
\vspace{-4pt}
\begin{itemize}[leftmargin=*]
  \item Design and maintain scalable backend solutions focused on APIs, clean architecture, performance, and reliability using Go, Node.js, TypeScript, Python, and PostgreSQL.
  \item Evolve CI/CD pipelines with Azure DevOps and infrastructure-as-code with Terraform, reducing manual deployment effort and increasing release predictability.
  \item Drive technical system design, module organization, architectural reviews, and internal pattern improvements to strengthen maintainability and long-term code evolution.
  \item Lead performance, reliability, and delivery quality initiatives, identifying bottlenecks and proposing solutions for production stability and lower response times.
  \item Partner with technical and business teams to translate complex requirements into scalable backend solutions, with clear communication and focus on impact.
\end{itemize}

\vspace{8pt}
\textbf{Celeste AI} — Software Developer \hfill Mar 2023 – Jul 2025 \\
São José dos Campos, Brazil
\vspace{-4pt}
\begin{itemize}[leftmargin=*]
  \item Designed and implemented backend services for an AI platform for automated meeting recording, transcription, summarization, and notification flows.
  \item Built asynchronous pipelines with queue-based orchestration and fault isolation, improving resilience across distributed services.
  \item Developed a calendar synchronization service integrating Google Calendar events with internal schedulers to provision meeting assistants before live sessions.
  \item Resolved complex distributed scheduling issues by normalizing time zones across containers, databases, and external APIs.
  \item Built a cost-optimization microservice that reduced storage usage by up to 80\% by extracting and standardizing audio tracks from video files before transcription.
  \item Integrated subscription plans, recurring billing, and usage-based packages, supporting monthly, annual, and on-demand models.
\end{itemize}

\vspace{8pt}
\textbf{Agenzia MKT} — Software Developer \hfill Mar 2022 – Feb 2023 \\
São José dos Campos, Brazil (Hybrid)
\vspace{-4pt}
\begin{itemize}[leftmargin=*]
  \item Developed and maintained backend services and APIs supporting business demands across production systems.
  \item Built integrations between internal and external systems, exposing and consuming APIs to automate processes and reduce manual operations.
  \item Improved existing systems by fixing issues, optimizing flows, and increasing operational stability and efficiency.
  \item Stack: Node.js, TypeScript, Python, React, Redis, RabbitMQ, SQL Server.
\end{itemize}

\vspace{8pt}
\textbf{Sistema Athos} — Software Developer \hfill Dec 2021 – Feb 2023 \\
Brazil
\vspace{-4pt}
\begin{itemize}[leftmargin=*]
  \item Developed and maintained backend routines and business-driven features supporting product evolution and client operations.
  \item Implemented and refactored modules in a mixed legacy/modern environment, improving organization, stability, and code quality.
  \item Investigated and resolved technical issues, reducing operational failures and increasing system reliability.
  \item Stack: Delphi 2010, Node.js, TypeScript, React, PostgreSQL 9.
\end{itemize}

\vspace{8pt}
\textbf{Sistema Athos} — Technical Support \hfill Dec 2020 – Dec 2021 \\
Caraguatatuba, Brazil
\vspace{-4pt}
\begin{itemize}[leftmargin=*]
  \item Provided technical support for installation, training, application maintenance, and database support at a commercial automation company.
  \item Identified critical issues in the NF-e issuance system, analyzed incidents, and documented permanent solutions later adopted internally to improve stability.
\end{itemize}

% ================= EDUCATION =================
\section*{Education}

\textbf{MBA in Software Engineering} — USP/Esalq \hfill Nov 2025 – Dec 2027 \\

\textbf{Data Science} — Pontifícia Universidade Católica de Campinas \hfill Aug 2023 – Oct 2023 \\

\textbf{B.Sc. in Software Engineering} — Estácio \hfill Aug 2022 – Aug 2025 \\

\textbf{B.Sc. in Law} — Centro Universitário Módulo \hfill Feb 2020 – Dec 2024 \\

% ================= ADDITIONAL =================
\section*{Additional Information}
Backend-focused engineer with strong ownership mindset, comfortable operating in ambiguous problem spaces, legacy systems, and high-impact technical challenges. Combines pragmatic problem-solving, clear communication, and product awareness with formal background in Law, Data Science, and Software Engineering.

\end{document}
